Titulo

### 2015-03-18 Paper/ms.tex
finished central galaxy model section

Our aim is to provide a realistic baseline to compare against
observations of LAES at $z\sim 3$. 
It has been found by analysis of the abundance and angular correlation
function that LAES reside in DM halos of masses in the range
$10^{10}-10^{11}$\Msun \cite{WalkerSoler2012}. 
This mass range corresponds to maximum circular velocities in the
range $60-125$\kms and a median halo scale radius of
$15$kpc. Considering that these galaxies are gas dominated we
approximate their neutral hydrogen gas contents has half their total
baryonic content estimated from the cosmological baryon to dark matter
abundances $\Omega_b/\Omega_{dm}=0.1825$ \citep{Planck2015}, which
gives us gaseous masses in the range $10^{9}-10^{10}$\Msun.

\footnote{These results were found using the N-body data
  available in \url{www.cosmosim.org}}.

From these constraints we chose to model our galaxies as sphere of
radius $15$kpc and rotation velocities in the range
$60-125$\kms.

>>>>

Our aim is to provide a realistic baseline to compare against
observations of LAES at $z\sim 3$. 
It has been found by analysis of the abundance and angular correlation
function that LAES reside in DM halos of masses in the range
$10^{10}-10^{11}$\Msun \cite{WalkerSoler2012}. 
This mass range corresponds to maximum circular velocities in the
range $60-125$\kms and a median halo scale radius of
$15$kpc.  \footnote{These results were
  found using the  N-body data available in \url{www.cosmosim.org}}.

These galaxies have gas fractions close to $20\%$
\citep{Narayanan2012}. We approximate that the hydrogen content is
$20\%$ the total baryonic content from the cosmological baryon to dark
matter  abundances $\Omega_b/\Omega_{dm}=0.1825$ \citep{Planck2015},
multiplied by a primordial Hydrogen fraction of $0.75$.
All these considerations gives us hydrogen masses in the range
$2.7\times 10^{8}-2.7\times 10^{9}$\Msun.

These choices give us a range for the number density of Hydrogen atoms
of $4\times10^{-4}-4\times 10^{-3}$ atoms cm$^{-3}$. 
With a Lyman-$\alpha$ cross section at the line center of
$\sigma_{H}=1.0\times 10^{-14}$ cm$^{2}$ we finally obtain that the
optical depth from the cloud's center  should be in the range $\tau=2
\times 10^{5} - 2 \times 10^{6}$.

From these constraints we chose to model two kinds of central galaxies
in the extremes of these distributions. The first has $\tau =2\times
10^5$ and a raotational velocity of $60$\kms. The second has
$\tau=2\times 10^6$ and a rotational velocity of $125$\kms.
